Generalization Errors of Hard Parameter Sharing: High-dimensional Asymptotics and Implications

### 2020-09-30 arxiv/examples.tex
revise

\begin{corollary}[Derived from Theorem \ref{thm_main_RMT}]\label{cor_MTL_loss}
	In the setting described above, assume further that a) the sample size $n_2$ of task two is greater than $(1 + \tau) p$, and b) there exists a small constant $c_0>0$ such that the signal-to-noise ratios satisfy 
	\be\label{choiceofpara0}
		p^{ c_0} \le \frac{p\kappa^2}{\sigma^2 }  \le p^{1-c_0},\quad  \frac{pd^2}{\sigma^2}=\OO(1).
	\ee
	%Let $B, A_1, A_2$ be the global minimum of equation \eqref{eq_mtl}. Then
	The prediction loss of the hard parameter sharing estimator for task two satisfies that
	\begin{align}\label{cor_MTL_error}
	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le 
	 & \left|L(\hat{\beta}_2^{\MTL}) -\frac{\sigma^2}{\rho_1+\rho_2-1} - pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right|  \le  \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2 ),
	 \end{align}
	 for any constant $c\in (0,c_0)$.
\end{corollary}

>>>>

\begin{corollary}[Derived from Theorem \ref{thm_main_RMT}]\label{cor_MTL_loss}
	In the setting described above, assume further that a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) there exists a small constant $c_0>0$ such that the signal-to-noise ratios satisfy 
	\be\label{choiceofpara0}
		p^{ c_0} \le \frac{\kappa^2}{\sigma^2 }  \le p^{1-c_0},\quad  \frac{d^2}{\sigma^2}=\OO(1).
	\ee
	%Let $B, A_1, A_2$ be the global minimum of equation \eqref{eq_mtl}. Then
	The prediction loss of the hard parameter sharing estimator for task two satisfies that
	\begin{align}\label{cor_MTL_error}
	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le 
	 & \left|L(\hat{\beta}_2^{\MTL}) -\frac{\sigma^2}{\rho_1+\rho_2-1} - pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right|  \le  \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2 ),
	 \end{align}
	 for any constant $c\in (0,c_0)$.
\end{corollary}

### 2020-09-30 arxiv/proof_examples.tex
revise

\subsection{The Random-Effects Model}\label{app_iso_cov}
We now give the proof of Proposition \ref{cor_MTL_loss}. As in the proof of Theorem \ref{thm_many_tasks}, we first derive a bias-variance decomposition of the prediction loss $L(\hat \eta_2^{\MTL})$. Then we can calculate the bias term and the variance term using Theorem \ref{thm_main_RMT}.

@@

		& = \left\| X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2 +\sigma^2(n_1+n_2-p).

@@

Using the concentration estimates in Lemma \ref{largedeviation}, we can control the difference between $g(A)$ and its partial expectation. %$\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2}$.
 \begin{claim}\label{claim_largedev1}
 In the setting of Proposition \ref{cor_MTL_loss}, we have that 
$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2}\right| \le p^{-c_\infty}\cdot p\left(\sigma^2 +\|\beta_1\|^2 +\|\beta_2\|^2 \right). $$
 \end{claim}
 \begin{proof}
 \todo{add proof}

@@

>>>>

\subsection{The Random-Effects Model}\label{app_iso_cov}

\paragraph{Proofs for two tasks.}  We now give the proof of Proposition \ref{cor_MTL_loss}. As in the proof of Theorem \ref{thm_many_tasks}, we first derive a bias-variance decomposition of the prediction loss $L(\hat \eta_2^{\MTL})$. Then we can calculate the bias term and the variance term using Theorem \ref{thm_main_RMT}.

@@

		& = \left\| X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-A\beta_2)\right\|^2 +A^2\left\| X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-A\beta_2)\right\|^2 +\sigma^2(n_1+n_2-p).

@@

@@

&\exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2} \\
&=[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(2)})^\top X^{(2)} \hat \Sigma^{-1}(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)}\right]\\
&+ A^2[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)}\right] +\sigma^2(n_1+n_2-p),
where we used that the entries of $\beta_1-A\beta_2\in \R^p$ are i.i.d. random variables with mean zero and variance $p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]$.

Using the concentration estimates in Lemma \ref{largedeviation}, we can control the difference between $g(A)$ and its partial expectation. %$\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2}$.
 \begin{claim}\label{claim_largedev1}
 In the setting of Proposition \ref{cor_MTL_loss}, we have that 
$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2 }\right| \le p^{-c_\infty}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right). $$
 \end{claim}
 \begin{proof}
 \todo{add proof}
 \end{proof}

Then we calculate the predication loss ...
